Convergence rate of MAP estimates \\ for the exponential family

### 2021-05-26 main.tex
Add more bias variance illustrations

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{figs/numerical_schema.pdf}
	\caption{A numerical illustration of the different characters featured in the bias-variance decomposition, for a 1D Gaussian $\cN(\mu, \sigma^2)$.}
	\label{fig:bias-variance-numerical}
\end{figure}

@@

\paragraph{No Mixed Term.}
In fact, it is possible to have no mixed term using the central point $\tilde \mu_n = \nabla \logpart(\E[\MAPt])$ instead of $\mu_n = \E[\MAPm]$,  exactly as described by \citet[Theorem 0.1]{pfau2013generalized}.
\begin{align}
	\expect{\bregmanconj(\mu^* ; \hat \mu_n)} 
	= \bias{\bregmanconj(\mu^* ; \tilde \mu_n)}
	+ \variance{\expect{\bregmanconj(\tilde \mu_n ; \MAPm)}}
\end{align}
Now the big question, is : what kind of results do I get with such quantities ? In general, it seems that $\tilde \mu_n$ is a very central and interesting quantity to consider.  We show these decompositions in Figure~\ref{fig:experimental_decomposition}.

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{{figs/biasvariance/ratio=0.8_n0=10}.pdf}
	\caption{
	\textbf{Left:} training curves and analytic upper bound. 
	\textbf{Center:} bias-mixed-variance decomposition, using the arithmetic mean.
	\textbf{Right:} bias-variance decomposition, using the harmonic mean.
	}
	\label{fig:experimental_decomposition}
\end{figure}

>>>>

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{figs/numerical_schema_n=3.pdf}
	\caption{A numerical illustration of the different characters featured in the bias-variance decomposition, for a 1D Gaussian $\cN(\mu, \sigma^2)$.}
	\label{fig:bias-variance-numerical}
\end{figure}

@@

\paragraph{No Mixed Term.}
In fact, it is possible to have no mixed term using the central point $\tilde \mu_n = \nabla \logpart(\E[\MAPt])$ instead of $\mu_n = \E[\MAPm]$,  exactly as described by \citet[Theorem 0.1]{pfau2013generalized}.
\begin{align}
	\expect{\bregmanconj(\mu^* ; \hat \mu_n)} 
	&= \bias{\bregmanconj(\mu^* ; \tilde \mu_n)}
	+ \variance{\expect{\bregmanconj(\tilde \mu_n ; \MAPm)}} \\
	\expect{\bregman(\MAPt; \natp^*)} 
	&= \bias{\bregman(\E[\MAPt]; \natp^*)}
	+ \variance{\expect{\bregman(\MAPt; \E[\MAPt])}} 
\end{align}
Now the big question, is : what kind of results do I get with such quantities ? In general, it seems that $\tilde \mu_n$ is a very central and interesting quantity to consider.  We show these decompositions for $\cN(0,\sigma^2)$ in Figure~\ref{fig:variance_decomposition} and  $\cN(\mu, \sigma^2)$ in Figure~\ref{fig:gaussian_decomposition}.

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{{figs/biasvariance/linear_ratio=0.8_n0=10}.pdf}
	\caption{
	\textbf{Gaussian variance $\cN(0,\sigma^2)$ example. Left:} training curves and analytic upper bound. 
	\textbf{Center:} bias-mixed-variance decomposition, using the arithmetic mean.
	\textbf{Right:} bias-variance decomposition, using the harmonic mean.
	}
	\label{fig:variance_decomposition}
\end{figure}

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{{figs/gaussians/log_n0=1}.pdf}
	\caption{
	\textbf{Full gaussian $\cN(\mu, \sigma^2)$ example. Left:} training curves and analytic upper bound. 
	\textbf{Center:} bias-mixed-variance decomposition, using the arithmetic mean.
	\textbf{Right:} bias-variance decomposition, using the generalized mean.
	}
	\label{fig:gaussian_decomposition}
\end{figure}
